Graphical representation example: Alternative interpretations

### 2023-11-23 notebooks/Graphical_representation_alternatives.Rmd
Explains how the chunk is adapted to compute the coordinates in the latent space by calling the new function and transforming the coordinates accordingly.

```{r compute-oblique-items-latent-space}
## Compute parameters and coordinates:
items_oblique_params <- items_M2PL |> compute_mirt_params(
  all_of(INTERCEPT_COLKEY), starts_with(DISCR_PREFFIX), # Input parameters
  cov_matrix = corr_matrix,                             # Input covariances
  dir_out    = c(COSINE_DIRTYPE, DEGREE_DIRTYPE)        # Output configuration
)
items_oblique_coords <- items_oblique_params |> compute_mirt_coords(
  D, MDISC, starts_with(COSINE_DIRTYPE),
  transform       = transform_matrix,
  original_coords = FALSE
)
items_oblique        <- full_join(
  items_oblique_params, items_oblique_coords,
  by = ITEM_COLKEY
)

>>>>

We now compute the coordinates in the latent space. In order to compute the
transformed coordinates, instead of the transformation matrix, I understand we
need its "complementary" with the same role in the latent space. That would be
the inverse transposed of that transformation matrix.

We return in this case the original coordinates (in the latent space) along with
the transformed ones (to rectangular coordinates).

```{r compute-oblique-items-latent-space}
## Compute parameters and coordinates:
items_oblique_params <- items_M2PL |> compute_mirt_params(
  all_of(INTERCEPT_COLKEY), starts_with(DISCR_PREFFIX), # Input parameters
  cov_matrix = corr_matrix,                             # Input covariances
  dir_out    = c(COSINE_DIRTYPE, DEGREE_DIRTYPE)        # Output configuration
)
items_oblique_coords <- items_oblique_params |> compute_mirt_coords(
  D, MDISC, starts_with(COSINE_DIRTYPE),
  transform       = transform_matrix_inv_transp,
  original_coords = TRUE
)
items_oblique        <- full_join(
  items_oblique_params, items_oblique_coords,
  by = ITEM_COLKEY
)
